Simulation

### 2018-12-13 simulation.Rmd
Small updates to language and formatting

---
title: "Simulation"
description: |
  A simulation study investigating resolution metrics in various conditions
author:
  - name: Matti Vuorre 
    affiliation: Columbia University
date: "`r Sys.Date()`"
output: 
  radix::radix_article:
    toc: true
    toc_depth: 2
    self_contained: false
    lib_dir: "site_libs"
bibliography: bibliography.bib
---

@@

# Preface

This simulation examines potential bias in measures of metacognitive resolution (gamma correlation and $d_a$) due to guessing.

@@

However, in a mAFC tasks, gamma will be downward biased as a function of m (number of response alternatives) [@schwartz1994methodological]. Below, we show in detail how guesses cause this bias.

## Example

@@

Here is example person A's table, observed gamma, and distribution

@@

```{r examples-more, eval = FALSE}
# Binary confidence
summary(replicate(100, vcdExtra::GKgamma(table(example(5, 1, 2, 10)))$gamma))
c <- tibble(
  accu = c(0,1,0,1,1,1),
  conf = c(1,2,3,4,5,6)
)
table(c)
vcdExtra::GKgamma(table(c))$gamma
```

# Simulation overview

This simulation produces hypothetical data sets of responses (accuracy & confidence rating pairs) under various conditions of guessing, performance, and underlying generative parameters defining primary task performance and metacognitive resolution. The simulation scheme is adapted from @benjamin2008measurement, and is outlined for one hypothetical subject as follows:

- A list of items is generated based on number of items, and probability of known items
- For each item, accuracy is determined such that known items are always correct, whereas unknown items are correct according to a defined guessing probability
- For each item, a "metacognitive evidence" value is generated from one of two gaussian distributions depending on whether the item was known or unknown
  - Unknown item evidence values: mean zero and standard deviation one
  - Known item evidence values: mean $\delta$ and standard deviation $\sigma_k$
- Evidence values are converted to confidence ratings (6-category scale) values via five thresholds
- Resolution metrics are obtained based on this simulated data set of accuracy values (0/1) and confidence (1-6) ratings

@@

```{r symbol-table}
tibble(
  Variable = c(
    "Number of trials/items", 
    "Proportion of known items (performance)",
    "Guessing proportion (i.e. 1/m)",
    "Mean of evidence distribution for known items",
    "SD of evidence distribution for known items",
    "Evidence thresholds"
  ),
  Symbol = c(
    "$N_{trials}$",
    "$P_{know}$",
    "$\\pi$",
    "$\\delta$",
    "$\\sigma_k$",
    "$\\tau$"
  ),
  `Default value` = c(
    100, 0.5, 0.0, 1.0, 1.0, "-1, -.5, 0, .5, 1"
  )) %>% 
  kable(
    escape = FALSE, 
    caption = "Summary of generative variables used in simulation function."
  )
```

Metacognitive resolution, defined as $\delta$, is then estimated with a number of metrics:

- Goodman-Kruskal *gamma* correlation
- Signal-detection metrics $y_0$ (y-intercept of the type-2 zROC) and $d_a$ [@benjamin2008measurement]
- Signal-detection metrics equivalent to above, but obtained from an ordinal regression [@BurknerOrdinalRegressionModels2018; @KnoblauchModelingPsychophysicalData2012], $d_{a-ord}$ and $d'_{ord}$
- Pearson correlation $r$

@@

## Example simulation run

@@

```{r sim-test, fig.cap="Example run of simulation scheme with $\\delta = 1$: Histogram of simulated confidence ratings split by accuracy."}
clm(
  ordered(con6) ~ factor(accuracy),
  link = "probit",
  scale = ~accuracy,
  control = list(maxIter = 100, convergence = "stop"),
  data = dat)$coef %>% t %>%
  kable(digits=2, caption = "Ordinal model parameters from aggregate data")
tmp <- sim_run(out="data", 
               d_gen = 1,
               p_know = .65,
               p_guess = 0.25,
               n_trials = nrow(dat))
metrics(tmp, confidence = NULL, ordinal=TRUE) %>% 
  kable(digits=2, caption = "Estimated metrics from example simulation run")
dat %>% 
  bind_rows(tmp, .id = "is_real") %>% 
  mutate(is_real = ifelse(is_real==1, "Real", "Simulated")) %>% 
  ggplot(aes(con6, fill = as.factor(accuracy))) +
  scale_fill_brewer("Accuracy", palette = "Set1") +
  scale_y_continuous("Count", 
                     expand = expand_scale(mult = c(0, .1))) +
  scale_x_continuous("Confidence", breaks = pretty_breaks(6)) +
  stat_count(aes(y=stat(count)),
             col="black", position = position_dodge()) +
  facet_wrap("is_real")
rm(tmp)
```

# Simulation

The aim of this simulation was to examine the impact of guessing on measures of resolution at various levels of performance and generative resolution.

## Method

@@

We ran the simulation over a range of values of $P_{know}$ and $\delta$. The simulation was repeated 100 times at each combination of the generative parameters, with 20000 trials for each repeat.

```{r sims-parameters-summary}
tibble(
  Variable = c(
    "Number of trials/items", 
    "Proportion of known items (performance)",
    "Guessing proportion (i.e. 1/m)",
    "Mean of evidence distribution for known items",
    "SD of evidence distribution for known items",
    "Evidence thresholds"
  ),
  Symbol = c(
    "$N_{trials}$",
    "$P_{know}$",
    "$\\pi$",
    "$\\delta$",
    "$\\sigma_k$",
    "$\\tau$"
  ),
  Values = c(
    20000, "0.05 - 0.95", "0 / 0.25", "0.05 - 2.45", 1.0, "-1, -.5, 0, .5, 1"
  )) %>% 
  kable(
    escape = FALSE, 
    caption = "Variable values used in main simulation run."
  )
```

@@

## Results

@@

```{r main-figure, layout="l-body-outset", fig.width=7, fig.height=5.8}
sims_long %>% 
  # filter(d_gen %in% delta_bins[seq(1, length(delta_bins), 2)]) %>% 
  rename(Guessing = p_guess, Parameter = parameter) %>% 
  ggplot(aes(p_know, estimate, col=d_gen, group=d_gen)) +
  scale_color_viridis_c("Resolution") +
  geom_line(size=.75) +
  scale_x_continuous("Performance", breaks = pretty_breaks(5), limits = 0:1) +
  scale_y_continuous("Mean estimate", breaks = pretty_breaks(5)) +
  facet_grid(Parameter~Guessing, scales="free_y", labeller=label_both) +
  theme(legend.position = "bottom")
```

@@

## Bias

@@

# Compare data to simulations

@@

```{r guessing-correct-plot, fig.cap = "Comparison of observed and corrected proportion corrected."}
# Illustrate guessing correction
dat_metrics %>% 
  ggplot(aes(p, p_know)) +
  geom_point(shape=1) +
  geom_abline(lty = 2) +
  coord_cartesian(ylim = 0:1, xlim = 0:1) +
  labs(x="Observed (proportion correct)", y="Corrected (performance)") +
  theme(aspect.ratio=1)
```

## Regression test

@@

```{r regression-test, layout="l-page", fig.width=8, fig.height=4, fig.cap="Comparison of observed correlations to simulation results."}
DEGREE <- 2
# PLot
tmp <- dat_metrics %>% 
  group_by(exp) %>% 
  summarise(d_ord = mean(d_ord, na.rm=T)) %>% 
  group_by(exp) %>% 
  mutate(d_gen = delta_bins[which.min(abs(d_ord - delta_bins))]) %>% 
  inner_join(sims_long) %>% 
  filter(p_guess == 0.25)
tmp %>% 
  ggplot(aes(p_know, estimate)) +
  scale_x_continuous("Performance", breaks = pretty_breaks(5)) +
  scale_y_continuous("Estimate", breaks = pretty_breaks(5)) +
  facet_grid(parameter~exp, scales="free") +
  theme(legend.position = "none") +
  geom_point(data = gather(dat_metrics, parameter, value, da, gamma), 
             aes(x = p_know, y = value), 
             col = "black", shape=1, size = .25, alpha = .5) +
  geom_smooth(data = gather(dat_metrics, parameter, value, da, gamma), 
              aes(x = p_know, y = value), lty=2, 
              formula = y ~ poly(x, DEGREE),
              method = "lm", span=2, size=.66, se=T, alpha=.33, col="black") +
  geom_smooth(method = "lm", aes(col=d_gen), se=F, 
              formula = y ~ poly(x, DEGREE)) +
  scale_color_viridis_c("Resolution", 
                        values = rescale(tmp$d_gen, 
                                         to = c(0, 1))) +
  theme(panel.spacing = unit(10, "pt"))

@@

# Replication of Benjamin and Diaz

We replicated the simulation of @benjamin2008measurement: For several levels of generative $\delta$, we ran 100 sim-subjects with 1000 trials each. For each subject, $P_{know}$ (known items) was drawn from $N(50, 10^2)$, rounded to an integer. Instead of 4 rating categories, we used 6 to more closely correspond to our data. $\pi$ (guessing) was varied at 0 and 0.25. $\sigma_k$ was either 1 or 1.5.

@@

```{r simsbd-plot1, layout="l-body-outset", fig.width=8, fig.height=6, fig.cap="Results from simulation replicating Benjamin and Diaz's (2008) simulation scheme when guessing=0. The two columns indicate different generative $\\sigma_s$s."}
sims_bd %>% 
  filter(p_guess == 0) %>% 
  gather(parameter, value, gamma, da, y0, da_ord, d_ord, r) %>% 
  group_by(parameter, d_gen, s_gen) %>% 
  summarise(n = n(), mean = mean(value, na.rm = T)) %>% 
  ggplot(aes(d_gen, mean, col = parameter)) +
  scale_color_brewer(
    "Parameter", 
    palette = "Dark2", 
    aesthetics = c("color", "fill")
    ) +
  geom_line(size=1.25) +
  geom_abline(lty=2, size = .33) +
  scale_x_continuous(expression(delta), breaks = pretty_breaks(5)) +
  scale_y_continuous("Mean estimate", breaks = pretty_breaks(5)) +
  facet_wrap("s_gen", labeller=label_both) +
  theme(aspect.ratio = 1)
```

The results of this simulation mirrored those of @benjamin2008measurement: Both gamma and $d_a$ are monotonically increasing with generative $\delta$, but only $d_a$ has the property of scaling linearly with $\delta$. Second, the SDT metrics are more accurately estimated via an ordinal regression [@KnoblauchModelingPsychophysicalData2012]. The $d'_{ord}$ metric recovers the generative parameter in every simulation, and its transformations ($d_{a-ord}$) are easily obtained and mirror those of the line-fitting procedure.

## Introducing guessing

@@

```{r simsbd-plot-guessing, layout="l-body-outset", fig.width=8, fig.height=6, fig.cap="Results from simulation replicating Benjamin and Diaz's (2008) simulation scheme when guessing=0.25. The two columns indicate different generative $\\sigma_s$s."}
sims_bd %>% 
  filter(p_guess == 0.25) %>% 
  gather(parameter, value, gamma, da, y0, da_ord, d_ord, r) %>% 
  group_by(parameter, d_gen, s_gen) %>% 
  summarise(n = n(), mean = mean(value, na.rm = T)) %>% 
  ggplot(aes(d_gen, mean, col = parameter)) +
  scale_color_brewer(
    "Parameter", 
    palette = "Dark2", 
    aesthetics = c("color", "fill")
    ) +
  geom_line(size=1.25) +
  geom_abline(lty=2, size = .33) +
  scale_x_continuous(expression(delta), breaks = pretty_breaks(5)) +
  scale_y_continuous("Mean estimate", breaks = pretty_breaks(5)) +
  facet_wrap("s_gen", labeller=label_both) +
  theme(aspect.ratio = 1)
```

@@

# Appendix A: Simulation function {.appendix}

@@

# Appendix B: Calculating gamma from ROC {.appendix}

>>>>

---
title: "Simulation"
description: |
  A simulation study investigating the impact of task knowledge and guessing on resolution metrics
author:
  - name: Matti Vuorre 
    affiliation: Columbia University
date: "`r Sys.Date()`"
output: 
  radix::radix_article:
    toc: true
    toc_depth: 2
    self_contained: false
    lib_dir: "site_libs"
bibliography: bibliography.bib
---

@@

## Preface

This simulation examines potential bias in measures of metacognitive resolution (gamma correlation and $d_a$) due to guessing and task knowledge.

@@

However, in mAFC tasks, gamma is downward biased as a function of m (number of response alternatives) [@schwartz1994methodological]. Below, we show in detail how guesses cause this bias.

### Example

@@

Here is example person A's table, observed gamma, and distribution of gammas over 1000 replications.

@@

## Simulation overview

This simulation produces hypothetical data sets of responses (accuracy & confidence rating pairs) under various conditions of guessing, performance, and true resolution. The simulation scheme is adapted from @benjamin2008measurement, and is outlined for one hypothetical subject as follows:

- A list of items is generated based on number of items, and proportion of known items (Knowledge = *K*)
- For each item, accuracy is determined such that known items are always correct, whereas unknown items are correct according to a defined guessing probability *G*
- For each item, a "metacognitive evidence" value is generated from one of two gaussian distributions depending on whether the item was known or unknown
  - Unknown item evidence values: mean zero and standard deviation one
  - Known item evidence values: mean *R* and standard deviation $\sigma_k$. Thus, R defines the generative resolution parameter as the difference between the evidence distributions.
- Evidence values are converted to confidence ratings (6-category scale) values via five thresholds
- Resolution metrics are obtained based on this simulated data set

@@

```{r symbol-table}
tibble(
  Variable = c(
    "Number of trials/items", 
    "Proportion of known items (knowledge)",
    "Guessing proportion (i.e. 1/m)",
    "Mean of evidence distribution for known items",
    "SD of evidence distribution for known items",
    "Evidence thresholds"
  ),
  Symbol = c(
    "$N_{trials}$",
    "$K$",
    "$G$",
    "$R$",
    "$\\sigma_k$",
    "$\\tau$"
  ),
  `Default value` = c(
    100, 0.5, 0.0, 1.0, 1.0, "-1, -.5, 0, .5, 1"
  )) %>% 
  kable(
    escape = FALSE, 
    caption = "Summary of generative variables used in simulation function."
  )
```

Metacognitive resolution, defined as *R*, is then estimated with a number of metrics:

- Goodman-Kruskal Gamma correlation
- Signal-detection metrics $y_0$ (y-intercept of the type-2 zROC) and $d_a$ [@benjamin2008measurement]
- Signal-detection metrics equivalent to above, but obtained from an ordinal regression [@BurknerOrdinalRegressionModels2018; @KnoblauchModelingPsychophysicalData2012], $d_{a-ord}$ and $d'_{ord}$
- Pearson correlation $r$

@@

### Example simulation run

@@

```{r sim-test, fig.cap="Example run of simulation scheme with $R = 1$: Histogram of simulated confidence ratings split by accuracy."}
tmp <- sim_run(
  out = "data", 
  d_gen = 1,
  p_know = .65,
  p_guess = 0.25,
  n_trials = nrow(dat)
)
metrics(tmp, confidence = NULL, ordinal=TRUE) %>% 
  kable(digits=2, caption = "Estimated metrics from example simulation run")
dat %>% 
  bind_rows(tmp, .id = "is_real") %>% 
  mutate(is_real = ifelse(is_real==1, "Real", "Simulated")) %>% 
  ggplot(aes(con6, fill = as.factor(accuracy))) +
  scale_fill_brewer("Accuracy", palette = "Set1") +
  scale_y_continuous("Count", 
                     expand = expand_scale(mult = c(0, .1))) +
  scale_x_continuous("Confidence", breaks = pretty_breaks(6)) +
  stat_count(aes(y=stat(count)),
             col="black", position = position_dodge()) +
  facet_wrap("is_real")
rm(tmp)
```

## Simulation

### Method

@@

We ran the simulation over a range of values of *K* and *R*. The simulation was repeated 100 times at each combination of the generative parameters, with 20000 trials for each repeat.

```{r sims-parameters-summary}
tibble(
  Variable = c(
    "Number of trials/items", 
    "Proportion of known items (knowledge)",
    "Guessing proportion (i.e. 1/m)",
    "Mean of evidence distribution for known items",
    "SD of evidence distribution for known items",
    "Evidence thresholds"
  ),
  Symbol = c(
    "$N_{trials}$",
    "K",
    "G",
    "R",
    "$\\sigma_k$",
    "$\\tau$"
  ),
  Values = c(
    20000, "0.05 - 0.95", "0 / 0.25", "0.05 - 2.45", 1.0, "-1, -.5, 0, .5, 1"
  )) %>% 
  kable(
    escape = FALSE, 
    caption = "Variable values used in main simulation run."
  )
```

@@

### Results

@@

```{r main-figure, layout="l-body-outset", fig.width=7, fig.height=5.8}
sims_long %>% 
  # filter(d_gen %in% delta_bins[seq(1, length(delta_bins), 2)]) %>% 
  rename(Guessing = p_guess, Parameter = parameter) %>% 
  ggplot(aes(p_know, estimate, col=d_gen, group=d_gen)) +
  scale_color_viridis_c("Resolution") +
  geom_line(size=.75) +
  scale_x_continuous("Knowledge", breaks = pretty_breaks(5), limits = 0:1) +
  scale_y_continuous("Mean estimate", breaks = pretty_breaks(5)) +
  facet_grid(Parameter~Guessing, scales="free_y", labeller=label_both) +
  theme(legend.position = "bottom")
```

@@

### Bias

@@

## Compare data to simulations

@@

```{r guessing-correct-plot, fig.cap = "Comparison of observed and corrected proportion corrected."}
# Illustrate guessing correction
dat_metrics %>% 
  ggplot(aes(p, p_know)) +
  geom_point(shape=1) +
  geom_abline(lty = 2) +
  coord_cartesian(ylim = 0:1, xlim = 0:1) +
  labs(x="Observed proportion correct", y="Corrected p(correct) ('knowledge')") +
  theme(aspect.ratio=1)
```

### Regression test

@@

```{r regression-test, layout="l-page", fig.width=8, fig.height=3.6, fig.cap="Comparison of observed correlations to simulation results."}
DEGREE <- 2
# PLot
tmp <- dat_metrics %>% 
  group_by(exp) %>% 
  summarise(d_ord = mean(d_ord, na.rm=T)) %>% 
  group_by(exp) %>% 
  mutate(d_gen = delta_bins[which.min(abs(d_ord - delta_bins))]) %>% 
  inner_join(sims_long) %>% 
  filter(p_guess == 0.25)
tmp %>% 
  ggplot(aes(p_know, estimate)) +
  scale_x_continuous("Knowledge", breaks = pretty_breaks(5)) +
  scale_y_continuous("Estimate", breaks = pretty_breaks(5)) +
  facet_grid(parameter~exp, scales="free_y") +
  theme(legend.position = "none") +
  geom_point(data = gather(dat_metrics, parameter, value, da, gamma), 
             aes(x = p_know, y = value), 
             col = "black", fill = "white", shape = 21, size = .5, alpha = .8) +
  geom_smooth(data = gather(dat_metrics, parameter, value, da, gamma), 
              aes(x = p_know, y = value), lty=2, 
              formula = y ~ poly(x, DEGREE),
              method = "lm", span=2, size=.66, se=T, alpha=.33, col="black") +
  geom_smooth(method = "lm", aes(col=d_gen), se=F, 
              formula = y ~ poly(x, DEGREE)) +
  scale_color_viridis_c("Resolution", 
                        values = rescale(tmp$d_gen, 
                                         to = c(0, 1))) +
  theme(panel.spacing = unit(11, "pt"))

@@

### Debias average gammas

Next, we approximated what the average gamma & da in each experiment would have been, if guesses were absent. We did this by taking the average gamma, da, and performance of each experiment, and finding their corresponding non-guessing values from the simulations.

```{r}
tmp <- dat_metrics %>% 
  group_by(exp) %>% 
  summarise(
    p_know = mean(p, na.rm = T),
    gamma = mean(gamma, na.rm = T), 
    da = mean(da, na.rm = T)
    ) %>% 
  group_by(exp) %>% 
  # Get the nearest performance used in simulations
  mutate(p_know = p_know_bins[which.min(abs(p_know - p_know_bins))]) %>% 
  ungroup() %>% 
  gather(parameter, mean_data_estimate, gamma, da)
tmp2 <- sims_long_bias %>% 
  filter(between(p_know, .65, .76))
# Take rows for each exp and parameter where distance between observed resolution value and estimated(guessing=0.25) is the smalles
full_join(tmp, tmp2) %>% 
  mutate(difference = abs(mean_data_estimate - p_guess0.25)) %>% 
  arrange(parameter, exp, difference) %>%
  distinct(parameter, exp, .keep_all = TRUE) %>% 
  select(exp, p_know, parameter, mean_data_estimate, p_guess0.25, p_guess0) %>% 
  mutate(percent_increase = (p_guess0-mean_data_estimate)/mean_data_estimate) %>% 
  group_by(parameter) %>% 
  mutate(mpc = mean(percent_increase)) %>% 
  kable(
    escape = FALSE, 
    digits = 2,
    caption = "Resolution metrics from data"
  )
```

### Test subjects against simulated curve at perfect metacognition

Here, we attempt to test observed gamma/da against perfect metacognition. Each participant's observed gamma/da is paired with the corresponding mean simulated estimate at maximum d_gen (corresponding to about gamma = .96) and guessing = 0.25 and the participant's level of performance.

```{r}
tmp1 <- dat_metrics %>% 
  select(exp, subject, gamma, da, p_know) %>% 
  group_by(exp, subject) %>% 
  mutate(p_know_bin = p_know_bins[which.min(abs(p_know - p_know_bins))]) %>% 
  ungroup()
tmp2 <- sims_mean %>% 
  filter(d_gen == max(delta_bins), p_guess == "0.25")
tmp <- left_join(tmp1, tmp2, by = c("p_know_bin" = "p_know"))
names(tmp) <- str_replace_all(names(tmp), "\\.x", ".data")
names(tmp) <- str_replace_all(names(tmp), "\\.y", ".perfect")
# Are subjects gamma/da significantly lower than the gamma/da from simulation with perfect metacognition? That is, we use the difference between each subject's gamma and the simulated perfect gamma at that subjects point of performance
t.test(tmp$gamma.perfect, tmp$gamma.data, paired = T)
t.test(tmp$da.perfect, tmp$da.data, paired = T)
p1 <- tmp %>% 
  mutate(
    gamma_diff = gamma.perfect - gamma.data,
    da_diff = da.perfect - da.data
  ) %>% 
  select(exp, subject, contains("_diff")) %>% 
  gather(key, value, gamma_diff, da_diff) %>% 
  ggplot(aes(value)) +
  geom_histogram(bins = 50) +
  facet_wrap("key", scales = "free")
p2 <- tmp %>% 
  ggplot(aes(gamma.perfect, gamma.data)) +
  geom_abline(lty = 2) +
  geom_point()
p3 <- tmp %>% 
  ggplot(aes(da.perfect, da.data)) +
  geom_abline(lty = 2) +
  geom_point()
(p3 | p2) / p1
```

## Replication of Benjamin and Diaz

We replicated the simulation of @benjamin2008measurement: For several levels of generative *R*, we ran 100 sim-subjects with 2000 trials each. For each subject, *K* was drawn from $N(50, 10^2)$, rounded to an integer. Instead of 4 rating categories, we used 6 to more closely correspond to our data. *G* was varied at 0 and 0.25. $\sigma_k$ was either 1 or 1.5.

@@

```{r simsbd-plot1, layout="l-body-outset", fig.width=8, fig.height=6, fig.cap="Results from simulation replicating Benjamin and Diaz's (2008) simulation scheme when guessing=0. The two columns indicate different generative $\\sigma_s$s."}
sims_bd %>% 
  filter(p_guess == 0) %>% 
  gather(parameter, value, gamma, da, y0, da_ord, d_ord, r) %>% 
  group_by(parameter, d_gen, s_gen) %>% 
  summarise(n = n(), mean = mean(value, na.rm = T)) %>% 
  ggplot(aes(d_gen, mean, col = parameter)) +
  scale_color_brewer(
    "Parameter", 
    palette = "Dark2", 
    aesthetics = c("color", "fill")
    ) +
  geom_line(size=1.25) +
  geom_abline(lty=2, size = .33) +
  scale_x_continuous(Resolution, breaks = pretty_breaks(5)) +
  scale_y_continuous("Mean estimate", breaks = pretty_breaks(5)) +
  facet_wrap("s_gen", labeller=label_both) +
  theme(aspect.ratio = 1)
```

The results of this simulation mirrored those of @benjamin2008measurement: Both gamma and $d_a$ are monotonically increasing with generative *R*, but only $d_a$ has the property of scaling linearly with it. Second, the SDT metrics are more accurately estimated via an ordinal regression [@KnoblauchModelingPsychophysicalData2012]. The $d'_{ord}$ metric recovers the generative parameter in every simulation, and its transformations ($d_{a-ord}$) are easily obtained and mirror those of the line-fitting procedure.

### Introducing guessing

@@

```{r simsbd-plot-guessing, layout="l-body-outset", fig.width=8, fig.height=6, fig.cap="Results from simulation replicating Benjamin and Diaz's (2008) simulation scheme when guessing=0.25. The two columns indicate different generative $\\sigma_s$s."}
sims_bd %>% 
  filter(p_guess == 0.25) %>% 
  gather(parameter, value, gamma, da, y0, da_ord, d_ord, r) %>% 
  group_by(parameter, d_gen, s_gen) %>% 
  summarise(n = n(), mean = mean(value, na.rm = T)) %>% 
  ggplot(aes(d_gen, mean, col = parameter)) +
  scale_color_brewer(
    "Parameter", 
    palette = "Dark2", 
    aesthetics = c("color", "fill")
    ) +
  geom_line(size=1.25) +
  geom_abline(lty=2, size = .33) +
  scale_x_continuous(Resolution, breaks = pretty_breaks(5)) +
  scale_y_continuous("Mean estimate", breaks = pretty_breaks(5)) +
  facet_wrap("s_gen", labeller=label_both) +
  theme(aspect.ratio = 1)
```

@@

## Appendix A: Simulation function {.appendix}

@@

## Appendix B: Calculating gamma from ROC {.appendix}
